\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{physics}
\usepackage{bbm}
\usepackage{graphicx}
\usepackage{varioref}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{amssymb}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{textcomp,geometry,graphicx,enumerate}
\usepackage[framemethod=tikz]{mdframed}
\usepackage{color}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{automata,positioning}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}
\usepackage{framed}
\usepackage{xcolor}

\usepackage[ampersand]{easylist}


%Easy list Defs
\include{Proofs/proof1}
\include{Proofs/proof2}
\include{Proofs/proof3}
\include{Proofs/proof4}
\include{Proofs/proof5}
\include{Proofs/proof6}
\include{projectQ}

\include{SipsersT/Sipser1}
\include{SipsersT/Sipser2}
\include{SipsersT/Sipser3}

%%Definition Styling
\newtheoremstyle{mydef}
{\topsep}{\topsep}%
{}{}%
{\bfseries}{}
{\newline}
{%
  \rule{\textwidth}{0.4pt}\\*%
  \thmname{#1}~\thmnumber{#2}\thmnote{\ -\ #3}.\\*[-1.5ex]%
  \rule{\textwidth}{0.4pt}}%

\theoremstyle{mydef}
\newtheorem{definition}{Definition}

%%Theorem Styling
\newtheoremstyle{mythm}
{\topsep}{\topsep}%
{}{}%
{\bfseries}{}
{\newline}
{%
  \rule{\textwidth}{0.4pt}\\*%
  \thmname{#1}~\thmnumber{#2}\thmnote{\ -\ #3}.\\*[-1.5ex]%
  \rule{\textwidth}{0.4pt}}%

\theoremstyle{mythm}
\newtheorem{theorem}{Theorem}

%%Lemma Styling
\newtheoremstyle{mylemming}
{\topsep}{\topsep}%
{}{}%
{\bfseries}{}
{\newline}
{%
  \rule{\textwidth}{0.4pt}\\*%
  \thmname{#1}~\thmnumber{#2}\thmnote{\ -\ #3}.\\*[-1.5ex]%
  \rule{\textwidth}{0.4pt}}%

\theoremstyle{mylemming}
\newtheorem{lemma}{Lemma}

%%Question Styling
\newtheoremstyle{myq}
{\topsep}{\topsep}%
{}{}%
{\bfseries}{}
{\newline}
{%
  \rule{\textwidth}{0.4pt}\\*%
  \thmname{#1}~\thmnumber{#2}\thmnote{\ -\ #3}.\\*[-1.5ex]%
  \rule{\textwidth}{0.4pt}}%

\theoremstyle{myq}
\newtheorem{question}{Question}



\title{Syntax will not lose semantics. Both will be defined always.}
\author{lina3866 }
\date{December 2020}

\begin{document}

\maketitle

\begin{abstract}

A supplement to Computer Science Courses which, writ large, explore content from and relating to Michael J. Sipser's lectures on the theory of computation, first taught at MIT.

\end{abstract}

\section{Introduction}

\subsection{Brief}

Wanky. %Sipser's starting text for the mathematical theory of computation is  well-received and oft-regarded indispensable. Its erst exploration and theorems pertaining important results on the necessary syntactic structures to construct 'theoretically computable (that is, machine-decideable)' semantic programming languages is a prolific work. Conceived to ensure mathematical closure and continue the efforts for a set-theoretical approach into... it's still Sipser's notation that's used in the forefront of theoretical computer science: see, for example, ``Quantum Turing-Machines Paper" (Bob Coecke, 2020 bla). It's clear that these new ideas extend directly from Sipser's diagrammatic inlay and initial approach.}  \\

\textbf{8 interesting questions and proofs}: In understanding their solutions, we'll have dissected examples which required mathematical rigour. The result: key learning objectives (and their associated styles of proof) of the Oxford course (\emph{Foundations of Computer Science:  2019-2020}),  recited Michelmas Term of 2020 by Dr Egor Kolomov, are challenged and composited. 
%%
\newpage

%%
\section{Regular Expressions and Context-Free Languages}
\\
\subsubsection{Chomsky Language Hierarchy}

Not every language is regular, and not every language is Turing-Decidable (TD). Languages are usually denoted by $L_{1}$, . Languages are composed of finite length strings of words $w$, each if these languages are de (that is, sets of finite words , composed of symbols from a finite sets which are recognised by DFAs, and by a theorem of equivalence also by NFAs)... easy easy ensure you say $\Gamma$ is ()$\alphabet$ or some shit. Must say that they can be inputted into a machine, which we'll see later as an algorithm after Church-Turing thesis (!).


Point is, here ensure: nothing is later just syntatic! V bad he will fuk.

Expressive power is a categorical way to measure how valuable languages are for computations. This is why NFAs and DFAs aren't as useful as Turing Machines (they're not even computers - probability does not influence how the same string is twice processed). 
\\
By Kleene's theorem we know regular expressions, $R$, describe the class of languages, $L(R)$, equivalent to the regular languages. 

\\but are not necessarily TD are called context-free languages (CFLs), and they are generated by the rules of a context-free grammar. Every context-free grammar can enforce its rules taking Chomsky Normal Form (CNF). 
\\
The Pumping Lemma for CFLs (similair not equal to the Pumping Lemma for Regular Languages), is not appropriate for proving a language is context free. There exist languages which pass the PL for CFLs: not all of these languages are CFLs (e.g.), . wever it is important to be aware: just because a language does not contradict the pumping lemma for CFLs does not ensure it really is a CFL.
\\
insery cirlces
\\
At the end of this chapter we'll prove \\
\qone
\\
\subsection{Regular Expressions and Q2}
\thmequiv

\defreg
\defkleene
\qtwo
\prooftwo

%\defconvex
\defpmpset
\thmarmstrong

\subsection{Pumping Lemma for Context-Free Languages}

\defcfg
\defcfl



\\
\subsubsection{Problem 1 - Modify Pumping Lemma for context-free Languages}
\thmpl
\vspace{10}
\\
Consider the language $L:=\left\{ a^{n}b^{n}c^{n\  }|\  n>0\right\}  $. We will prove (by contradiction) $L$ is not context-free using the pumping lemma. 
\\\textbf{\textit{Proof}}:
 Assume $L$ is context free. By the Theorem \ref{theorem:cfldef}, this means an integer $p$ exists (the pumping length), $s.t.$ for the string $s \in L$, $s=a^{p}b^{p}c^{p}$, the following must hold:
\\
$s=uvwxy$, where each of $u,v,w,x,y$ are all substrings in $L$ and
\\
1. for each integer $i \geq 0$, $uv^{i}wx^{i}y\in L$
\\
2. $|vx| \geq 1$, and 
\\
3. $|vwx| \leq p$
\\
Strings of the form $s=a^{p}b^{p}c^{p}$ restrict choices of $vwx$ to 5 considerations:
\\
\begin{enumerate}
    \item $vwx=a^{j}\  with\  some\  j\leq p$
    \item $vwx=a^{j}b^{k}\  with\  some\  j,k\  s.t.\  j+k\leq p$
    \item $vwx=b^{j}\  with\  some\  j\  s.t.\  j\leq p$
    \item $vwx=b^{j}c^{k}\  with\  some\  j,k\  s.t.\  j+k\leq p$
    \item $vwx=c^{j}\  with\  some\  j\leq p$
\end{enumerate}
\\
Suppose $i \neq 1$, then we should have $uv^{2}wx^{2}y \in L$. This is clearly not the case, for none of the 5 permitted string formulas above are of the form $a^{i}b^{i}c^{i\  }$ for $i=2$, because $uv^{i}wx^{i}y$ contains a different number of letters $a,b,$ and $c$ in each of the 5 cases above (do it). 
\\
This contradicts the initial assumption $L$ is context free.
\\
Consider now the language $L_{2}:=\left\{ a^{j}b^{k}c^{l\  }|\  j,k,l\in \mathbb{N} \right\}  \cup \left\{ a^{i}b^{j}c^{j}d^{j}\  |\  i,j\in \mathbb{N} \  ,\  i\geq 1\right\}  $, $L_{2}$ is not a CFL but does not contradict the pumping lemma, in fact strings $s \in L_{2}$ of the form $s=b^{j}c^{k}d^{l} $ with $j \geq 1$ will suffice to prove the first question:
\\
To give an example of a non-trivial class of langauges for which the 'modified pumping lemma' holds, and furthermore an infinite class $s.t.$ the complement is also infinite, we look no further than (Zach Tomaszewski): 
\\
$L_{d}:=\left\{ ww\  |\  w\in \left\{ a,b\right\}^{+}  \right\}  $ is not a context free language; it's complement $\bar{L}_{d} =\left\{ strings\  w\  over\  \left\{ a,b\right\}  \  |\  w\  is\  not\  of\  the\  form\  ww,\  where\  w\in \left\{ a,b\right\}^{+}  \right\}  $ is indeed context-free. Define +, and finish proof. Clearly infinite class. Now need pushdown automata to prove $L_{d}$ NOT CFL..
\\
We see $\barL_{d}$ is a context-free language by constructing the follownig grammar:

\\
S → E|U|ε E → AB|BA A → ZAZ|a B → ZBZ|b U → ZUZ|Z Z → a|b
\\

should have enough here now. need tidy finish trim cite.
\newpage
\subsection{\small{Problem \ 1.} \normalsize\textit{Proof}}
 \vspace{25}\\
\qone 
\proofone
\\
\newpage
We know every DFA is equivalent to an NFA from ch.1 Sip and Dr K. Also, we know every regular expression is equivalent, via some combination of language operators which enjoy closure under the class, regular languages $L$, which are decided by some deterministic finite automaton (DFA) (up to having ?1 'violation' of the pumping lemma for regular languages? check.). For those  =
\\
\thmtrytch

\newpage

\\
\defpa
\\
\newpage
%%

\subsection{\small{Problem \ 2.} \normalsize\textit{Proof}}
\qtwo
\prooftwo
%%
{Sipser3}
\newpage
\section{Turing}
\deftm
\deftrecdec
\deftape
\defnwa
\thmsavage
%%
{proof3}
\newpage
\subsection{\small{Problem \ 3.} \normalsize\textit{Proof}}
\qthree
\proofthree
\newpage
 \begin{definition}[Halting Problem] \label{Sipser p243}[M. Sipser, p243]
  Let’s consider a related problem, HALT TM , the problem of determining whether a Turing machine halts (by accepting or rejecting) on a given input. This problem is widely known as the halting problem. 
\[ HALT_{TM}=\left\{ \left< M,\  w\right>  \  |\  M\  is\  a\  TM\  and\  M\  halts\  on\  input\  w\right\}  \]
\end{definition}
\\
\begin{theorem}[Halting Theorem] \label{Sipser p243}[M. Sipser, p243] \newline
$HALT_{TM}$ is undecidable.
 \end{theorem}
\\
 \begin{theorem}[Rice Theorem]
 Place
 \end{theorem}
\\
\begin{theorem} \label{Sipser p209}[M. Sipser, p209] \newline
A language is decidable iff it is Turing-recognizable and co-Turing-recognizable.
\end{theorem}
$Remark:$ \ A language is decidable exactly when both it and its complement are Turing-recognizable.
\\

 \qfour
 \\
{proof5}
\qfive
\\
{proof6}
\qsix
\proofsix
\\
\qseven
\\
\qeight


\section{P, NP, NP-Hard, and NP-Complete}

\afterthree


\newpage
{afterflow}
\end{document}